### 2025-07-11 pca.qmd
20250708 - track chunk execution times
20250711 - players highest and loading on each PCA component

@@

```{r}
pca3ComponentOblique$scores[which.max(pca3ComponentOblique$scores[,1]),]
dataMerged[which.max(pca3ComponentOblique$scores[,1]), c("player_display_name", "season", "week", component1vars)]

pca3ComponentOblique$scores[which.min(pca3ComponentOblique$scores[,1]),]
dataMerged[which.min(pca3ComponentOblique$scores[,1]), c("player_display_name", "season", "week", component1vars)]
```

```{r}
pca3ComponentOblique$scores[which.max(pca3ComponentOblique$scores[,2]),]
dataMerged[which.max(pca3ComponentOblique$scores[,2]), c("player_display_name", "season", "week", component2vars)]

pca3ComponentOblique$scores[which.min(pca3ComponentOblique$scores[,2]),]
dataMerged[which.min(pca3ComponentOblique$scores[,2]), c("player_display_name", "season", "week", component2vars)]
```

```{r}
pca3ComponentOblique$scores[which.max(pca3ComponentOblique$scores[,3]),]
dataMerged[which.max(pca3ComponentOblique$scores[,3]), c("player_display_name", "season", "week", component3vars)]

pca3ComponentOblique$scores[which.min(pca3ComponentOblique$scores[,3]),]
dataMerged[which.min(pca3ComponentOblique$scores[,3]), c("player_display_name", "season", "week", component3vars)]
```

>>>>

```{r}
dataMergedWithPCA <- cbind(dataMerged, pca3ComponentOblique$scores)
```

@@

```{r}
dataMergedWithPCA %>% 
  arrange(-TC1) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component1vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC1) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component1vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC2) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component2vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC2) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component2vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(-TC3) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component3vars))
```

```{r}
dataMergedWithPCA %>% 
  arrange(TC3) %>% 
  head %>% 
  select(player_display_name, season, week, all_of(component3vars))
```
